---
title: "Assignment – Web APIs"
author: "ZIXIAN LIANG"
date: "2024-03-21"
output: 
  html_document:
     toc: true
     toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Introduction

The goal of this task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame.





```{r include=FALSE}
library(jsonlite)
library(tidyverse)
library(httr)
library(reactable)
```


## Data Acquisition

I focused on articles related to "Cars".


```{r include=FALSE}
api_key <- "8ZG2VBuoomcee7cmOCGAEazy6MAOVQ99"
```


```{r}
url <- "https://api.nytimes.com/svc/search/v2/articlesearch.json"
query <- list(q = "Cars", `api-key` = api_key)

response <- GET(url, query = query)
```



```{r}
data <- fromJSON(content(response, "text", encoding = "ISO-8859-1"))
```


## Data Organization

I selected columns provide essential information which are the main headline, original contributors, news desk, abstract, and source URL of the articles.


```{r}
cardata <- as.data.frame(data$response$docs)
column_data <- cbind(cardata$headline$main,cardata$byline$original,cardata$news_desk,cardata$abstract,cardata$web_url)
car <- as.data.frame(column_data)
colnames(car) <- c("Headline", "Contributors", "News desk", "Abstract", "Source")
```



## Conclusion


I've successfully built an interface in R to retrieve JSON data and convert it into an R DataFrame. Interactive table is generated as shown below.



```{r}
reactable(car, bordered = TRUE, striped = TRUE, highlight = TRUE, 
          filterable = TRUE,  showPageSizeOptions = TRUE, 
          pageSizeOptions = c(5, 10), defaultPageSize = 5)
```


